---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# seinfitR:  Modeling the Relationship Between Nematode Densities and Plant Growth

Authors:

Deoclecio Amorim - amorim@cena.usp.br, CENA-USP

João Novoletti - joao.novoletti@gmail.com

The goal of seinfitR is to fit the Seinhorst equation to experimental data describing the relationship between preplant nematode densities and plant growth using nonlinear least squares fitting.


## Installation

You can install the development version of seinfitR from [GitHub](https://github.com/dslabcena/seinfitR) with:

``` r
# install.packages("pak")
pak::pak("dslabcena/seinfitR")
```

## Basic Use

The syntax of seinfitR is straightforward, with the main function being seinfitR(...).

## Example

Modeling plant response to nematode densities using the "glasshouse" dataset:

```{r example}
library(seinfitR)

data(glasshouse, package = "seinfitR")


# Fit the model
model <- seinfitR(p_i = "p_i", y = "y", data = glasshouse,
                  start = list(m = 6, t = 6),
                  control = seinfitR_control(maxiter = 20), z_fixed = TRUE)

# View model summary
summary(model)
```

The seinfitR package provides some methods for model evaluation and visualization:

```{r methods}
# Print model coefficients
print(model)

# Extract variance-covariance matrix
vcov(model)

#Extract model coefficients
coef(model)

# Calculate R-squared
r_squared(model)

# Calculate Plot
plot(model)
```

Methods Available for seinfitR Objects
```{r show_methods}
methods(class = "seinfitR")
```
License

The seinfitR package is licensed under the GNU General Public License, version 3, see file LICENSE.md. © 2025 Deoclecio J. Amorim & João Novoletti.
